---
title: "FARS2 Vignette"
author: "Anne Cunningham"
date: "4 March 2018"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette demonstrating the use of the FARS2 package to analyse road fatalities}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(FARS2)
```

## The FARS2 package

The FARS2 package has been written to let you analyse data on road fatalities from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System.

As an end user, the only two functions you are likely to want to use are **fars_summarize_years** and **fars_map_state**.

## fars_summarize_years
This function needs to be supplied with a vector of years for which you have FARS data:
```{r fars_summarize_years}
fars_summarize_years(c(2013,2014))
```

## fars_map_state
This function needs to be supplied with a valid state number and a year:
```{r fars_map_state}
fars_map_state(40,2013)
```
